### 2015-07-15 fundamentals/impl.tex
fixes build error from missing curly brace
used some emphasis to reduce jargon-y nature of the various terms

A modular, \acrfull{ABM} approach is ideal for solving the coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: cluster-ready software and dynamic libraries.  The
\gls{ABM} framework is then described, focusing on its implementation and benefits
in a fuel cycle context. A discussion of the
time-dependent treatment of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
repository, provides a fundamental set of agent archetypes for basic simulation
functionality within \Cyclus.  Since \Cyclus relies on external
archetypes to represent the agents within a simulation, \Cycamore provides the
basic archetypes a new user needs to get started running simple simulations.
These archetypes support a minimal set of fuel cycle simulation goals and
provide, by example, a guide to new developers who would seek to contribute
their own archetypes outside of \Cycamore.

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$. 
\label{tab:cycamore}
\end{table}

@@

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
\Class{Composition}), in a material. The
\Class{Enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the \gls{SWU} and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

>>>>

A modular, \acrfull{ABM} approach is ideal for solving the coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies which arise in \Cyclus. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: \emph{cluster-ready software} and \emph{dynamically
loadable libraries}.  The
\gls{ABM} framework is then described, focusing on its implementation and benefits
in a fuel cycle context. A discussion of the
time-dependent treatment of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
repository, provides a fundamental set of dynamically loadable libraries
providing agent archetypes for basic simulation
functionality within \Cyclus.  Since \Cyclus relies on external
archetypes to represent the agents within a simulation, \Cycamore provides the
basic archetypes a new user needs to get started running simple simulations.
These archetypes support a minimal set of fuel cycle simulation goals and
provide, by example, a guide to new developers who would seek to contribute
their own archetypes outside of \Cycamore.

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table}

@@

The \Cyclus toolkit provides two useful interfaces for querying physical parameters of \Class{Material}
objects. First, the \Class{MatQuery} tool
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, etc. (i.e., a
\Class{Composition}), in a material. The
\Class{Enrichment} tool provides an \gls{API} for determining enrichment-related
parameters of a material, including the \gls{SWU} and natural
uranium required to enrich a material provided knowledge of feed, product, and tails
assays.

### 2015-07-15 fundamentals/intro.tex
used some emphasis to reduce jargon-y nature of the various terms

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, requiring
calculation of lifetime fuel costs and electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions these metrics are derived from
mass balances and facility operation history calculated by a fuel cycle
simulator. For example, where nuclear waste repository burden is derived from
ejected fuel masses, water pollution or land use can be derived from facility
operational histories (as in \cite{poinssot_assessment_2014}).

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while capabilities for tracking transformations in
material isotopics and the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way, having elected to neglect isotopic resolution in favor of
integral effects.

>>>>

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, a
combination of fuel and operating costs normalized by electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions, these metrics are derived from
mass balances and facility operation histories calculated by a fuel cycle
simulator. For example, where nuclear waste repository burden is derived from
ejected fuel masses, water pollution or land use can be derived from facility
operational histories (as in \cite{poinssot_assessment_2014}).

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Some
simulators were designed to model a single aspect of the fuel cycle in great
detail while neglecting others. For example, a simulator created for policy
modeling might have excellent capability in economics while capabilities for
tracking transformations in material isotopics and the effects of isotopics on
technology performance are neglected.  The \gls{CAFCA}\cite{guerin_impact_2009}
simulator is problem-oriented in this way, having elected to neglect isotopic
resolution in favor of integral effects.
